Interactive Markdown to explore Clustering

### 2017-06-09 src/ClusterComparison.Rmd
added scripts for choosing clustering method back in and dynamicCluster takes distance matrix form asDis now

inputPanel(
	   selectInput("dm", label = "Dissimilarity",
		       choices= c("euclidean","pearson","spearman"), selected="pearson"),

@@

#Visualize Dendrograms
clustering <- reactive({
    dynamicCluster(t(m.sub), dm=input$dm,
				 lk=input$lk,
				 ds=as.numeric(input$ds),
				 output="Cluster",
				 minSize=15)
})

>>>>

inputPanel(
	   selectInput("dm", label = "Dissimilarity",
		       choices= c("euclidean","pearson","spearman"), selected="euclidean"),

@@

#Visualize Dendrograms
clustering <- reactive({
    dis <- asDis(m.sub,dm=input$dm)
    dynamicCluster(dis, lk=input$lk,
			ds=as.numeric(input$ds),
			output="Cluster",
			minSize=15)
})
